---
title: "Results II"
output:
  ioslides_presentation:
    incremental: true
---

```{r, include = FALSE}
source("test-lab-3.R")
library(knitr)
library(tidyverse)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```
    

## Training MSE

```{r fig.align='center'}
results %>%
  filter(setting == "train") %>%
  ggplot(aes(x = reorder(group, MSE), 
             y = MSE, 
             shape = model_type)) + 
  geom_point(size = 3) +
  ylim(c(0, .03)) +
  xlab("Group") + 
  ylab("train MSE") + 
  theme(text = element_text(size = 16)) +
  scale_shape_manual(values = c(1, 16)) +
  theme_bw()
```


## Testing MSE

```{r fig.align='center'}
results %>%
  filter(setting == "test") %>%
  ggplot(aes(x = reorder(group, MSE), 
             y = MSE, 
             shape = model_type)) + 
  geom_point(size = 3) +
  xlab("Group") + 
  ylab("train MSE") + 
  theme(text = element_text(size = 16)) +
  scale_shape_manual(values = c(1, 16)) +
  theme_bw()
```


## Bias - Variance Tradeoff

```{r fig.align='center'}
results %>%
  filter(setting == "train") %>%
  ggplot(aes(x = p, 
             y = MSE, 
             shape = model_type)) + 
  geom_point(size = 3) +
  xlab("p") + 
  ylab("train MSE") + 
  theme(text = element_text(size = 16)) +
  scale_shape_manual(values = c(1, 16)) +
  theme_bw()
```

## Bias - Variance Tradeoff

```{r fig.align='center'}
results %>%
  filter(setting == "test") %>%
  ggplot(aes(x = p, 
             y = MSE, 
             shape = model_type)) + 
  geom_point(size = 3) +
  xlab("p") + 
  ylab("test MSE") + 
  theme(text = element_text(size = 16)) +
  scale_shape_manual(values = c(1, 16)) +
  theme_bw()
```



# Model Selection

## Activity (also on your problem set) {.smaller}

Using the `glmnet` package, construct a ridge regression and LASSO model to predict violent crime in the training data set. A description for how to use this package can be found in your book on page 251 and 255.

a. How many variables were selected by the LASSO?
b. What is the training MSE for ridge and LASSO using the optimal value of $\lambda$?
b. If the MSE's differed, why do you think one is higher than the other in this setting?

