---
title: "Results"
output:
  ioslides_presentation:
    incremental: true
---

```{r, include = FALSE}
source("test-lab-3.R")
library(knitr)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

## Scoring 
- Coding errors were corrected
- For each group, calculate
    - train MSE
    - test MSE on full test data set
- Remember: sampling variability!
    

## Training MSE

```{r fig.align='center'}
library(ggplot2)
ggplot(results, aes(x = reorder(group, MSE_train), y = MSE_train)) + 
  geom_point(size = 3) +
  ylim(c(0, .03)) +
  xlab("Group") + 
  ylab("train MSE") + 
  theme(text = element_text(size = 16))
```


## Testing MSE

```{r fig.align='center'}
ggplot(results, aes(x = reorder(group, MSE_test), y = MSE_test)) + 
  geom_point(size = 3) +
  ylim(c(0, .03)) +
  xlab("Group") + 
  ylab("test MSE") + 
  theme(text = element_text(size = 16))
```


## Bias - Variance Tradeoff

```{r fig.align='center'}
res2 <- results
names(res2)[c(3, 4)] <- c("MSE", "MSE")
res2 <- rbind(res2[, 1:3], res2[, c(1, 2, 4)])
res2$data <- c(rep("train", n_groups), rep("test", n_groups))
res2 <- filter(res2,
               MSE < .075)
ggplot(res2, aes(x = p, y = MSE, color = data)) +
  geom_line() +
  scale_x_log10()
```


## Variable usage {.build}

In the top 4 models, the types of variables were used.

### Twice
poverty, median income, urban

### Thrice
illegal immigration, race

### Fource
kids with two parents


# Model Selection

## Activity {.smaller}

Use the `leaps` package and the `regsubsets()` function to perform model selection on the crimes data set. Start with forward selection to `nvmax = 25`. The general form of the function is:

```
regsubsets(y ~ ., data = train, nvmax = 25, method = "forward")
```

Notes:

- You will need to do some `select()`ing before you can toss the training data set in there.
- Try investigating the output of this function by plotting it using `plot()` and calling on its `attributes()` and `str()`ucture.
- If you complete forward selection, try backwards and compare.
- If you complete both and have a sense of a good model, fit it and compute it's test MSE.

